---
title: 'DS 202 - Homework #2'
author: "Quita Jackson"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Swiss Banknotes

1.  Download the RMarkdown file with these homework instructions to use as a template for your work. Make sure to replace "Your Name" in the YAML with your name.
2.  The R package `mclust` contains a data set called `banknote`, consisting of (physical) measurements on 200 Swiss bank notes, 100 of which are genuine, while the other half is counterfeit. Load this data set (you might have to install the package) using the code below.

```{r message=FALSE}
# install.packages("mclust")
library(mclust) # if this throws an error of the form 'there is no package called mcmclust', uncomment the line above, run it once, then comment the line out again and run the code chunk again.
data(banknote)
```

3.  (1 pt) Use one of our object inspecting functions and interpret the result in the data that you see. 
>head(banknote) 
# This shows the 6 records of the dataset

4.  (1 pt) Use the package `ggplot2` to draw a barchart of `Status`. Map `Status` to the fill color of the barchart.
```{r}
# Draw barchart
library(ggplot2)
ggplot(banknote, aes(x = Status, fill= Status)) + 
  geom_bar()
```
  
  
This is a bar chart with Status as the x variable. Y defaults to the count of status and status is mapped to fill color. This plot just that we the data has 100 counterfeit and 100 genuine Swiss bank notes. There is an even amount of both types of bank notes. 

5.  (1 pt) Use the package `ggplot2` to draw a histogram of one of the variables in the dataset that shows a distinction between genuine and counterfeit banknotes. Use fill color to show this difference. Choose the binwidth such that there are no gaps in the middle range of the histogram.
```{r}
# Draw Histogram
ggplot(banknote, aes(x= Diagonal, fill= Status)) +
     geom_histogram(binwidth=.25)
```

This plot is a histogram with Diagonal as the x variable and Status as the fill color. This plot shows that geniune banknotes almost always have a bigger diagonal than counterfeit bank notes. It looks there there are, however some genuine banknotes that have a shorter diagonal than the counterfeit banknote's largest diagonal. 

6.  (1 pt) Use the package `ggplot2` to draw a scatterplot of two (continuous) measurements, color by `Status`. Find a pair of measurements that allow you to separate perfectly between genuine and counterfeit banknotes.
```{r}
# Draw Scatterplot
ggplot(banknote, aes(x=Length, y= Diagonal, color= Status)) +
  geom_point()
```
  
This plot is a scatter plot that used Length as the X and Diagonal as the Y with status as the color. This plot shows even though when the lengths for counterfeit and genuine banknotes are the same, the diagonal of genuine banknotes are higher. Some of the lengths of counterfeit bank notes are much larger than the other data points (Above 216.0), yet their diagonal is lower than those of the genuine banknotes. 

7.  (4.5 pts) For each of the three figures above, write a three sentence summary, describing the

    a.  **structure of the plot**: what type of plot is it? Which variables are mapped to x, to y, and to the (fill) color?
    b.  **main message of the plot**: what is your main finding, i.e. what do you want viewers to learn from the plot?
    c.  **additional message**: point out anomalies or outliers, if there are any.
#Done After each code chunk 

8.  (1.5 pts) Ensure that your submission is reproducible. We will load your Rmd file into RStudio and knit it. This should match your submitted html/word file

For the submission: submit your solution in an R Markdown file. Also submit the corresponding html/word file with it.

